A Compiler-Driven Optimization Approach\\to Solving Partial Differential Equations

### 2014-02-11 paper/bare_conf.tex
Add skeleton of the paper

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{An Optimizing Compiler for Finite Element Assembly}

@@

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill January 11, 2007

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

\section{Conclusion}
The conclusion goes here.

>>>>

\documentclass[conference]{IEEEtran}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A Compiler-Driven Optimization Approach\\to Solving Partial Differential Equations}

@@

\section{Introduction}
What we do in computational science. Applications motivating our study. The programming model of lizst and op2: ``simple'' kernels applied to sets of mesh elements. The need for optimizing such kernels. Contributions of the paper:
\begin{itemize}
\item A \textbf{compiler-driven} optimisation approach that can be generalised to a wide variety of kernels employed in many computational science codes. The key feature common to these kernels is that they usually fit the L1 cache of commodity processors.
\item Automation of such code optimizations in a framework for the resoloution of partial differential equations through the Finite Element Method, called Firedrake. This allows us to perform an in-depth performance evaluation of the proposed optimization strategy in real-world computations.
\end{itemize}

\section{Background}
Here we discuss about the computational characteristics of computational science kernels. Briefly cite op2 kernels. Emphasis on Finite Element Assembly. Generalization and formalization of a Finite Element Assembly kernel using quadrature representation.

\section{A Compiler-driven Approach to Code Optimization}
All the work done in the polyhedral model should be useful, but our kernels fit L1, so they need special attention for what concerns key aspects like managing registers, exploiting ILP in its various forms, and reducing loop overhead. 
Follows a description of code transformations using our compiler-driven approach.

\section{The PyOP2 Compiler}
Design and structure of the PyOP2 Compiler. Show the steps through which the IR is transformed (need to cite Firedrake here). Briefly describe a simple cost model that allows us to prune the space of code transformations.

\section{Performance Evaluation}
Performance evaluation. We show all of the results got so far and we explain them. We demonstrate the claim that a compiler-driven approach is necessary to obtain maximum performance. Also, our results prove that current vendor compilers still have notable limitations, despite optimizing loop nests that are 1) affine, 2) have no stencil, and 3) ?

\section{Related Work}
Show other work of people working on optimizations for computational science kernels. Inter-kernel vectorisation paper from Istvan. Previous work in FFC. Spencer et-al + Shin et. al. attempt to optimize computations that could benefit from using BLAS, but in practice they don't, due to the very small dgemm operations employed. Saday's model-driven SIMD code vectorisation for the tensor contraction engine.

\section{Conclusions}

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.

@@
